\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-08 paper.tex
Reached the orthorhombic lattice

The effective conductivity of the relatively thin sample in contact
with the grounded counterelectrode is large enough that we may assume its
surface $z=0$ is an equipotential.
On the other hand, no current can go across the insulating walls of
the cell, situated at $x=0$, $x=a$,, $y=0$ and $y=b$, nor through the
free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson
equation with a point charge source
\begin{equation}
  \label{eq:poisson}
  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),
\end{equation}
with mixed boundary conditions
\begin{equation}
  \label{eq:ground}
  \varphi(x,y,0)=0,
\end{equation}
and
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
,z)=E_{{_z}}(x, y ,c)=0.
\end{equation}
This problem may be solved readily using image charge theory
\notaL{ref}. The potential within the electrolytic cell coincides the
the field within an infinite vacuum containing the point charge
$q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
charges. The images include a reflection on the conducting bottom of the
cell, of the opposite charge $-q_0$ and situated at $(x_0, y_0,-z_0)$,
to guarantee that the bottom stays at potential zero.
There are further images on the four walls of the cell, of the same charge $q_0$
and situated at $(-x_0,Y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
them. Similarly, there is an image of the same charge $q_0$ at
$(x_0,y_0,2c-z_0)$ to guarantee that no current goes across the
surface of the electrolyte. Furthermore, each image charge has to be
further reflected by each of the aforementioned surfaces, yielding new
images.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{paper-1}
  \caption{Top view of the electrolytic cell (light blue) showing the charge at the
    tip of the electrode (red dot) and its images on the walls of the
    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
    $y=0,b$. The relation of some charges and their images is
    indicated by dashed arrows, with a bar to indicate the
    corresponding reflecting wall. The system may be interpreted as a
    periodic lattice with a rectangular unit cell of size $2a\times 2b$,
    one of which is indicated  by wide dashed lines, and with a basis of four equal
    charges at $(\pm x_0, \pm y_0, z_0)$.}
  \label{fig:topview}
\end{figure}
In Fig. \ref{fig:topview} we illustrate the real charge and all of
its images within the plane $z=z_0$. They form a periodic rectangular
lattice with a unit cell of size $2a\times 2b$ and with a basis of
four equal charges situated at the positions $\bm r_0$, $\bm
r_1=(-x_0, y_0, z_0)$, $\bm r_2=(x_0, -y_0, z_0)$ and $\bm r_3=(-x_0,
-y_0, z_0)$. In Fig. \ref{fig:sideview} we show a lateral view of the
image charges.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{paper-2}
  \caption{Side view of the electrolytic cell (light blue)
    showing the charge at the tip of the electrode (red dot), its
    images within the plane $z=z_0$ (blue dots), and its images at the
    surface of the sample and the top of the electrolyte (green
    dots). We use solid dots to denote particles with the same charge
    as that corresponding to the tip $q_0$, and open dots for those of
    opposite charge. The system may be interpreted as a periodic
    lattice with a rectangular unit cell of size $2a\times 4c$, one of
    which is indicated by wide dashed lines, and with a basis of four
    charges $q_0$ and another four charges $-q_0$.}
  \label{fig:sideview}
\end{figure}

This has a mixture of Dirichlet-Neumann type boundary conditions. By
using the simplified prism geometry  can solve the problem using the
theory of image loads. Each load has an image of the same sign and
magnitude for each lateral insulating surface and the opposite sign
change in the lower part of the conductive plane, as follows.
 \begin{figure}
 \centering
 \includegraphics[scale=.6]{Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
     real charge in the corner of the cell with its charges ($ q $)
     images of the same sign in $ Z_0 $ and another charge image ($ -q
     $) with change of sign located below the conductor in position $
     -Z_0 $. b) The upper face seen from above, a real load and its
     image loads in $ Z_0 $. c) All this formed a systems of a real
     load and its image loads produced by the cell walls and its other
     images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $)
in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic
box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a
reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$
due to a reflection in $ (x, 0, z) $ y the image of the image in
$\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then,
these four charges are reflected on the other two surfaces and the
eight new images are reflected on the original surface, etc.,
producing a periodic 2D rectangular network with unit cells of signs $
L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This
entire network is reflected from the bottom with an opposite sign load
(below the driver). Periodic copies separated by the vacuum in the $
xy $ plane whose area is being increased to achieve convergence.

>>>>

The effective conductivity of the relatively thin sample in contact
with the grounded counterelectrode is large enough that we may assume its
surface $z=0$ is an equipotential.
On the other hand, no current can go across the insulating walls of
the cell, situated at $x=0$, $x=a$,, $y=0$ and $y=b$, nor through the
free surface of the liquid at $z=c$. Thus, the problem to solve is Poisson's
equation with a point charge source
  \label{eq:poisson}
  \nabla^2\varphi=-4\pi q_0\delta(\bm r-\bm r_0),
with mixed boundary conditions
  \label{eq:ground}
  \varphi(x,y,0)=0,
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b
,z)=E_{{_z}}(x, y ,c)=0.
This problem may be solved readily using image charge theory
\notaL{ref}. The potential within the electrolytic cell coincides the
the field within an infinite vacuum containing the point charge
$q_0$ at the tip of the electrode at $\bm r_0$, and an array of its fictitious image
charges. The images include a reflection on the conducting bottom of the
cell, of the opposite charge $-q_0$ and situated at $(x_0, y_0,-z_0)$,
to guarantee that the bottom stays at potential zero.
There are further images on the four walls of the cell, of the same charge $q_0$
and situated at $(-x_0,Y_0,z_0)$, $(x_0,-y_0, z_0)$, $(2a-x_0, y_0,
z_0)$ and $(x_0, 2b-y_0,z_0)$ to guarantee that no current goes across
them. Similarly, there is an image of the same charge $q_0$ at
$(x_0,y_0,2c-z_0)$ to guarantee that no current goes across the
surface of the electrolyte. Furthermore, each image charge has to be
further reflected by each of the aforementioned surfaces, yielding new
images.
  \includegraphics[width=\textwidth]{paper-1}
  \caption{Top view of the electrolytic cell (light blue) showing the charge at the
    tip of the electrode (red dot) and its images on the walls of the
    rectangular cell, the images of its images and so on (blue dots). The walls are at $x=0,a$,
    $y=0,b$. The relation of some charges and their images is
    indicated by dashed arrows, with a bar to indicate the
    corresponding reflecting wall. The system may be interpreted as a
    periodic lattice with a rectangular unit cell of size $2a\times 2b$,
    one of which is indicated  by wide dashed lines, and with a basis of four equal
    charges at $(\pm x_0, \pm y_0, z_0)$.}
  \label{fig:topview}
In Fig. \ref{fig:topview} we illustrate the real charge and all of
its images within the plane $z=z_0$. They form a periodic rectangular
lattice with a unit cell of size $2a\times 2b$ and with a basis of
four equal charges situated at the positions $\bm r_0$, $\bm
r_1=(-x_0, y_0, z_0)$, $\bm r_2=(x_0, -y_0, z_0)$ and $\bm r_3=(-x_0,
-y_0, z_0)$. In Fig. \ref{fig:sideview} we show a lateral view of the
image charges.
  \includegraphics[width=\textwidth]{paper-2}
  \caption{Side view of the electrolytic cell (light blue)
    showing the charge at the tip of the electrode (red dot), its
    images within the plane $z=z_0$ (blue dots), and its images at the
    surface of the sample and the top of the electrolyte (green
    dots). We use solid dots to denote particles with the same charge
    as that corresponding to the tip $q_0$, and open dots for those of
    opposite charge. The system may be interpreted as a periodic
    lattice with a rectangular unit cell of size $2a\times 4c$, one of
    which is indicated by wide dashed lines, and with a basis of four
    charges $q_0$ and another four charges $-q_0$.}
  \label{fig:sideview}
Each plane of charges upon reflection on the surface of the sample yields an
plane of image charges of the opposite sign, while reflections
on the surface of the liquid yields a plane of charges of the same
sign. The side view may be interpreted as a periodic rectangular
lattice with a unit cell of size $2a\times 4c$ containing a basis of eight point
charges, four positive and four negative. A projection onto the $yz$
plane would similarly yield a rectangular lattice with a  $2b\times4c$
unit cell. Putting everything together, the problem is that of solving
Poisson's equation within an orthothombic lattice of size
$2a\times2b\times4c$ with a basis of 16 point charges arranged in
positive and negative planes.
